Novel lattice Boltzmann method for simulation of strongly shear thinning viscoelastic fluids

### 2024-06-22 NovelLBM.tex
comments in main doc

The spatio-temporal dynamics of the polymer stress $\ma{\tau}$ is given by equation~(\ref{eq:polymerStress}) in the form of an advection-reaction equation.
We solve this equation by a finite-volume scheme running in parallel (with identical time step) to the LBM solver.\RR{ For this, the simulation volume is subdivided in $1\times1\times1$ (in LU) cubes centered around each lattice node. The average value of $\ma{\tau}$ within these volumes is takes as the value at the lattice node.}
Advection is handled using the corner transport upwind scheme \cite{kuron2021}. \SG{ add two phrases about CTU which somewhat non-standard }
\RR{ The remaining derivatives are calculated using finite differences.} 
At the walls\RR{, which coincide with the surfaces of the finite volumes}, a zero-flux boundary condition for the stress is used.
The source terms are integrated using the Euler method.

@@

	For simple forces we use the algorithm presented by Guo et al. \cite{guo2002}.  \SG{ what are ''simple forces''? }

>>>>

The spatio-temporal dynamics of the polymer stress $\ma{\tau}$ is given by equation~(\ref{eq:polymerStress}) in the form of an advection-reaction equation.
We solve this equation by a finite-volume scheme running in parallel (with identical time step) to the LBM solver.\RR{ For this, the simulation volume is subdivided in $1\times1\times1$ (in LU) cubes centered around each lattice node. The average value of $\ma{\tau}$ within these volumes is takes as the value at the lattice node.}
Advection is handled using the corner transport upwind scheme\RR{ (CTU)} \cite{kuron2021}.\RR{ CTU considers the finite volume cell to be virtually displaced by $\vec{u}\Delta t$, where $\vec{u}$ is the local velocity and $\Delta t$ is the size of a time step. The resulting overlap with the neighboring cells (as a fraction of the cell volume) dictates what percentage of the polymer stress currently located at the cell is advected to the respective neighbor. This scheme prevents checkerboard instabilities.} \SG{ add two phrases about CTU which somewhat non-standard }\RK{done}
\RR{ The remaining derivatives are calculated using finite differences.}
At the walls\RR{, which coincide with the surfaces of the finite volumes}, a zero-flux boundary condition for the stress is used.
The source terms are integrated using the Euler method.

@@

	For forces we use the algorithm presented by Guo et al. \cite{guo2002}.  \SG{ what are ''simple forces''? }\RK{as opposed to stresses which are generalized forces. -> removed the "simple"}
